\section{Market}
At this point, it might be worth to take a closer look at the market that we're dealing with.
\subsection{Competitive Landscape}
\begin{itemize}
	\item \textbf{BIC} --- Undoubtedly, the company most often associated with modern disposable lighters.
		Whilst the production of disposable devices is not the main focus of {\fw}, it is their innovative
		wooden design that ultimately renders this outcome inevitable. The average price of a \textbf{BIC} sits
		at a unit price of around $1.50$\euro. With an estimated production price of $0.25${\euro} per unit,
		the lighters come at a sale margin of approximately $83\%$ (= $\frac{1.5 - 0.25}{1.5} \cdot 100$) and
		come at a great turnover rate.
	\item \textbf{Zippo} --- Unlike the former, \textbf{Zippo} focues on more premium market, with higher-quality
		products designed with longevity in mind. Fittingly, the price of the company's lighters aligns with the
		premium philosophy. With the lower-end prices at about $25${\euro} and the high-end peaking
		at just below $500${\euro}, the company provides a very wide spectrum of products for various types of
		customers.
\end{itemize}
It is important to note that, due to the philosophical differences between the two companies, their businesses do not
necessarily interfere with each other. The aspiration of {\fw} to aim at the higher-end of the market puts the business
outside of \textbf{BIC}'s competitive influences. Moreover, our business does not infringe on the specialties of \textbf{Zippo}
due to our highly-specialized target demographics and design philosophy (see UVP).
\subsection{Growth Trends}
According to a study\footnote{https://www.grandviewresearch.com/industry-analysis/pocket-lighter-market-report}
by \textit{Grand View Research}, the size of the market for pocket lighters was estimated at
around \textit{USD} $\:6,755.5$ \textit{million} in $2024$ and is projected to grow at a rate of $2.9\%$ annually from
$2025$ to $2030$.
\subsection{Design Trends}
According to the same study, there is an ongoing change in the behaviour of customers on the market:
\begin{quote}
	Modern consumers are increasingly gravitating towards multi-functional lighters that integrate features such
	as built-in LED lights, safety mechanisms, and ergonomic designs
\end{quote}
Additionally, a separate finding cited in the study hints at the potential viability of {\fw} on the lighter market:
\begin{quote}
	Moreover, the rise of lighter brands that emphasize eco-friendliness and sustainability is making a significant
	impact. [...] lighters made from biodegradable materials [...] are gaining traction.
	As consumers become more environmentally conscious, manufacturers are pivoting their
	efforts towards producing more sustainable alternatives, which reflects a broader societal shift towards greener
	products
\end{quote}
